\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
started writing proofs, made them compact

The graph processing algorithm is executed locally by a node (line 10 of \cref{fig:deps-set-algo3}). It must compute the value of $\opn{c-struct}\left( g_p \right)$, as defined in \cref{lindef}.
Its key property is \cref{lemma1}. 
We assume that processes initially agree, for each set of commands $\mathcal{D}$, on a total order $<_{\mathcal{D}}$ on $\mathcal{D}$.
In practice, if commands are attached a unique identifier among a totally ordered set, $<_{\mathcal{D}}$ can be the restriction of this total order to $\mathcal{D}$.

@@

\begin{mylemma}\label{lemma1}
Assume that $g_1$ and $g_2$ are two dependency graphs, 
that for every pair of non-commutative commands $c_1,c_2 \in V\left(g_2\right)$, either $\left( c_1,c_2 \right)\in E\left( g_2 \right)$ or $\left( c_2,c_1 \right)\in E\left( g_2 \right)$,
that $g_1$ and $g_2$ are compatible,
that $l_1$ is a linearization of $g_1$, and that $l_2$ is a linearization of $g_2$. 
Then we have (a), $\bot\bullet l_1$ and $\bot\bullet l_2$ are compatible c-structs, and (b), if $g_1 = g_2$ then $\bot\bullet l_1 = \bot\bullet l_2$.
\end{mylemma}

@@

\subsection{Consistency and Liveness}

\begin{mylemma}\label{lemma-compat}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible.
\end{mylemma}
\Cref{lemma-compat} follows from the safety property (b) of the map-agreement algorithm and definition of the graph $g_p$.
From (b) it follows that if $c$ is in the domain of both $m_p$ and $m_q$ then $m_p\left[ c \right] = m_q\left[ c \right]$.

>>>>

The graph processing algorithm is executed locally by a node (line 10 of \cref{fig:deps-set-algo3}). It must compute the value of $\opn{c-struct}\left( g_p \right)$, as defined in \cref{lindef}.
Its key property is \cref{lemma:graph}. 
We assume that processes initially agree, for each set of commands $\mathcal{D}$, on a total order $<_{\mathcal{D}}$ on $\mathcal{D}$.
In practice, if commands are attached a unique identifier among a totally ordered set, $<_{\mathcal{D}}$ can be the restriction of this total order to $\mathcal{D}$.

@@

\begin{mylemma}\label{lemma:graph}
Assume that $g_1$ and $g_2$ are two dependency graphs, 
that for every pair of non-commutative commands $c_1,c_2 \in V\left(g_2\right)$, either $\left( c_1,c_2 \right)\in E\left( g_2 \right)$ or $\left( c_2,c_1 \right)\in E\left( g_2 \right)$,
that $g_1$ and $g_2$ are compatible,
that $l_1$ is a linearization of $g_1$, and that $l_2$ is a linearization of $g_2$. 
Then we have (a), $\bot\bullet l_1$ and $\bot\bullet l_2$ are compatible c-structs, and (b), if $g_1 = g_2$ then $\bot\bullet l_1 = \bot\bullet l_2$.
\end{mylemma}

@@

\subsection{Consistency and Liveness}
Let us now sketch why our generic leaderless algorithm meets the consistency and liveness requirements of generalized consensus. Consider an execution of the algorithm.
\begin{mylemma}\label{lemma:compat}
If $g_p^1$ is the graph $g_p$ at time $t_1$, $g_q^2$ is the graph $g_q$ at time $t_2$, then $g_p^1$ and $g_q^2$ are compatible.
\end{mylemma}
%\vspace{-5pt}
\begin{proof*}
Follows from the safety property (b) of the map-agreement algorithm and definition of the graph $g_p$.
From (b) it follows that if $c$ is in the domain of both $m_p$ and $m_q$ then $m_p\left[ c \right] = m_q\left[ c \right]$.
\end{proof*}
%\vspace{-5pt}
\begin{mylemma}
    The consistency property always holds.
    \label{lemma:consistency}
\end{mylemma}
%\vspace{-5pt}
\begin{proof*}
    By \cref{lemma:compat} and the safety property (b) of the dependency-set algorithm, $g_p^1$ and $g_q^2$ satisfy the premises of \cref{lemma:graph}. Therefore we get that $g_p^1$ and $g_q^2$ are compatible.
\end{proof*}
